Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
Minor

@@

@@

Max values for alpha diversity `r diversities$max %>% pull(estimate)
								  %>% abs %>% max %>% round(., 2)` and
								  `r diversities$mmin %>%
								  pull(estimate) %>% abs %>% max %>%
								  round(., 2)`.

@@

```{r Reading maaslin lacto output}
maas.lacto.results.df.signf <- read.table("maaslin_lacto/maaslin_lacto_merged_phfinrisk_genus.txt", header=TRUE, sep='\t') %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  beta = Coefficient) %>%
   dplyr::filter(Qval < 0.05)

maas.lacto.signf.features <- maas.results.df.signf %>%
    pull(Feature) %>%
    as.character() %>%
    gsub("_", ".", .)

df.lacto.merged <-  merge.pheno.abu(pseq.lacto)
```

>>>>

unlink("maaslin_core", recursive = TRUE)

@@

unlink("maaslin_lacto", recursive = TRUE)

@@

@@

```{r Reading maaslin lacto output}
maas.lacto.results.df.signf <- read.table("maaslin_lacto/maaslin_lacto_merged_phfinrisk_genus.txt", header=TRUE, sep='\t') %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  beta = Coefficient) #%>%

colnames(maas.lacto.results.df.signf)
maas.lacto.results.df.signf %>%
    select(Variable, Feature, P.value, Q.value) %>%
    arrange(Q.value) %>%
    kable
```
